Figures

### 2025-08-31 code/08_figures-tables.Rmd
Code checked & formatted; html rendered

# Visualising location and bird species

I am using the figure code from here and adapting it for my needs..

Mentesana, L., Hau, M., D'Amelio, P.B., Adreani, N.M. and Sánchez-Tójar, A. (2025), Do Egg Hormones Have Fitness Consequences in Wild Birds? A Systematic Review and Meta-Analysis. Ecology Letters, 28: e70100. <https://doi.org/10.1111/ele.70100>

Code here: `https://github.com/ASanchez-Tojar/meta-analysis_egg_hormones_and_fitness/blob/main/code/003_figures.R`

```{r message=FALSE, warning=FALSE}
## Let's get the needed packages
if (!requireNamespace("devtools", quietly = TRUE))
    install.packages("devtools")

if (!requireNamespace("orchaRd", quietly = TRUE))
    devtools::install_github("daniel1noble/orchaRd", ref = "main")

pacman::p_load(ggplot2,dplyr,stringr,readr,cowplot,maps)

## Let's first get the data in for this plot

# Loading cleaned dataset
dataset_analysis<- read_csv(here::here("data/04_data_analysis/dataset_analysis.csv"))

```{r location-map}

# To split population_ID into location and country
dataset_analysis[c('Location','Country')] <- str_split_fixed(dataset_analysis$population_ID, ',', 2)

### For the purpose of this map, I am adding the the longitude and latitude of the study area manually. They exist in the dataset_analysis$population_location as they were extracted from the paper. I have also added some by just searching the general location since the coordinates were not provided for these..

data_coordinates<-data.frame(Location = unique(dataset_analysis$Location),
                             Lat_Location=c(51.50,38.41,40.45,
                                            45.40,52.39, 37.18,
                                            54,39.05,
                                            51.57,48,42.54,39.95,
                                            40.13,28.10,52.06,60.39),
                             Long_Location=c(19.29,-9.02,-3.50,
                                             -64.10,6.05,-3.11,
                                             -124,-76.81,
                                             -2.26,11,8.91,-75.16,
                                             -8.27,107.10,8.25,5.32))

## Let's now merge the datasets by the location names

dataset_analysis <- dataset_analysis %>%
  left_join(data_coordinates, by = "Location")

## Count how many times each Location appears in the full dataset
location_counts <- dataset_analysis %>%
  group_by(Location) %>%
  summarise(size.freq = n_distinct(paper_ID), .groups = 'drop')

@@

# create world map using ggplot() function 
# geom_map() function takes world coordinates as input to plot world map 
fig_map <- ggplot(world_coordinates, aes(x = long, y = lat)) + 
  geom_map(map = world_coordinates, 
    aes(map_id = region), 
    color = "white", fill= "#D9EAF7") + 
  geom_point(data = dataset_analysis_unique_rows, 
             aes(x = Long_Location, y = Lat_Location,
                 size = size.freq, colour=bird_species), alpha = 0.6) +
scale_size(range = c(3, 5)) +
  scale_fill_manual(values = c("#00B0BE","#FFB255",  "#FF8CAE", 
                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +

  scale_colour_manual(values = c("#00B0BE","#FFB255",  "#FF8CAE", 
                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
  guides(size = "none", alpha = "none") +
  labs(x = "Longitude",
       y = "Latitude",
       col = "Bird Species")+
  theme_classic() +
  theme(legend.position = c(0.99, 0.15),
        legend.justification = c("right", "bottom"),
        legend.background = element_rect(fill = "white", color = "black"),
        legend.text = element_text(size=6),
        axis.title = element_text(size = 10),
        axis.text.x = element_text(size = 10),
        axis.text.y = element_blank())

# To add the zoomed in map.. to show the points more clearly
zoom_map <- ggplot() + 
  geom_map(data = world_coordinates, map = world_coordinates,
           aes(map_id = region),
           color = "white", fill = "#D4D4D4") +
  geom_point(data = dataset_analysis_unique_rows,
             aes(x = Long_Location, y = Lat_Location,
                 size = size.freq, colour = bird_species),
             alpha = 0.9) +
  scale_size(range = c(2, 4)) +
  scale_colour_manual(values = c("#00B0BE","#FFB255",  "#FF8CAE", 
                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
  coord_cartesian(xlim = c(-10, 20), ylim = c(25, 65)) +  # Northern Hemisphere
  theme_void() +
  theme(
    legend.position = "none",
    plot.background = element_rect(color = "white", fill="white"),
    panel.border = element_rect(colour = "black", fill = NA, size = 1)
  )

geographic_distribution <- ggdraw() +
  draw_plot(fig_map) +
  draw_plot(zoom_map, x = 0.05, y = 0.15, width = 0.28, height = 0.38) + theme(panel.border = element_rect(colour = "black", fill=NA, size=1.5))

ggsave(here::here("figures/Figure_Distribution.png"), plot = geographic_distribution, height = 100, width = 170, units= 'mm', dpi = 600)
```

# Visualizing author network

```{r}
# # Loading cleaned dataset
# dataset_analysis<- read_csv(here::here("data/03_data_cleaning/dataset_analysis.csv"))
# 
# library(tidyverse)
# library(tidyr)
# library(igraph)
# installed.packages("ggraph")
# library(ggraph)
# 
# clean_author <- function(name) {
#   name %>%
#     str_replace_all(",", "") %>%   # remove commas
#     str_squish() %>%              # remove excess whitespace
#     str_to_title()                # standardize case (optional, if needed)
# }
# 
# # Apply cleaning to first and last author fields
# author_roles <- dataset_analysis %>%
#   distinct(paper_ID, .keep_all = TRUE) %>%
#   select(paper_ID, authors, bird_species) %>%
#   mutate(
#     author_list = str_split(authors, ";\\s*"),
#     first_author = map_chr(author_list, 1),
#     last_author = map_chr(author_list, ~ tail(.x, 1))
#   )%>%
#   mutate(
#     first_author=case_when(
#       first_author == "Polo, V" | first_author == "Polo V" ~ "Polo V.",
#       first_author == "Soler J J" ~ "Soler J. J.",
#       first_author == "Glądalski, M" ~ "Gladalski M.",
#       first_author == "Gwinner, H" | first_author == "Gwinner H" ~ "Gwinner H.",
#       TRUE ~ as.character(first_author)
#     ))%>%
#   mutate(
#     last_author=case_when(
#       last_author == "Veiga J P" ~ "Veiga J. P.",
#       TRUE ~ as.character(last_author)
#     )
#   )
# 
# # 2. Create Core Author Pairs (First → Last)
# author_pairs_core <- author_roles %>%
#   select(paper_ID, first_author, last_author) %>%
#   rename(from = first_author, to = last_author) %>%
#   filter(from != to) %>%
#   count(from, to, name = "weight")
# 
# # 3. Build Author Graph
# author_graph <- graph_from_data_frame(author_pairs_core, directed = TRUE)
# 
# # 4. Assign Dominant Bird Species to PIs (last authors)
# author_species <- author_roles %>%
#   select(last_author, bird_species) %>%
#   group_by(last_author, bird_species) %>%
#   count() %>%
#   slice_max(n, n = 1) %>%
#   distinct(last_author, .keep_all = TRUE)
# 
# # Add species as vertex attribute
# V(author_graph)$bird_species <- author_species$bird_species[
#   match(V(author_graph)$name, author_species$last_author)
# ]
# 
# # 5. Optional: Scale node size by number of papers per author
# author_paper_counts <- author_roles %>%
#   pivot_longer(cols = c(first_author, last_author), names_to = "role", values_to = "author") %>%
#   count(author, name = "paper_count")
# 
# # Add paper count attribute
# V(author_graph)$paper_count <- author_paper_counts$paper_count[
#   match(V(author_graph)$name, author_paper_counts$author)
# ]
# 
# # Replace NAs with small size for isolated authors
# V(author_graph)$paper_count[is.na(V(author_graph)$paper_count)] <- 1
# 
# # 6. Plot with ggraph
# ggraph(author_graph, layout = "fr") +
#   geom_edge_link(aes(width = weight), alpha = 0.4, color = "grey50") +
#   geom_node_point(aes(color = bird_species, size = paper_count)) +
#   geom_node_text(aes(label = name), repel = TRUE, size = 3) +
#   scale_edge_width(range = c(0.3, 2)) +
#   scale_size(range = c(3, 10)) +
#   theme_void() +
#   labs(title = "Author Collaboration Network by Bird Species",
#        size = "Paper Count") +
#   theme(legend.position = "right")
#

# Intercept only model

@@

```{r orchard plot for intercept only models}
pacman::p_load(here,tidyverse,metafor,orchaRd,patchwork,cowplot)

# Loading models for SMDH and lnRR

intercept_lnRR<-readRDS(here::here("model/intercept_lnRR.rds"))
intercept_SMDH<-readRDS(here::here("model/intercept_SMDH.rds"))

# Plot for lnRR

intercept_lnRR_plot<- orchaRd::orchard_plot(intercept_lnRR,
                                             mod = "1",
                                             group = "paper_ID",
                                             trunk.size = 0.3,
                                             branch.size = 2,
                                             twig.size = 0.5,
                                             alpha = 0.2,
                                             xlab = "Effect size (lnRR)", 
                                             fill =  T) +
  scale_fill_manual(values = "#98C127") +
  scale_colour_manual(values = "#98C127" ) +
theme_minimal(base_size = 14) +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
    legend.position = c(0.98, 0.05),
    legend.justification = c(1, 0),
    legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_blank()
  ) +
  labs(x = "Intercept")

# Plot for SMDH
intercept_SMDH_plot <- orchaRd::orchard_plot(intercept_SMDH,
                                    mod = "1",
                                    group = "paper_ID",
                                    trunk.size = 0.3,
                                    branch.size = 2,
                                    twig.size = 0.5,
                                    alpha = 0.2,
                                    xlab = "Effect size (SMDH)",
                                    fill = TRUE) +
  scale_fill_manual(values = "#F47A00") +
  scale_colour_manual(values = "#F47A00") +
  theme_minimal(base_size = 14) +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
    legend.position = c(0.98, 0.05),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_blank()
  ) +
  labs(x = "Intercept")

# Combine using patchwork
Figure_intercept <- intercept_lnRR_plot / intercept_SMDH_plot +
  plot_annotation(tag_level = c("A","B"))

ggsave(here::here("figures/Figure_overall_effect.png"), plot = Figure_intercept, height = 150, width = 170, units = "mm", dpi = 600)

###----------------------------------------------------------------------------------

## Now the cropped versions presented in the main manuscript..

###----------------------------------------------------------------------------------

intercept_lnRR_plot_crop <- orchaRd::orchard_plot(intercept_lnRR,
                                             mod = "1",
                                             group = "paper_ID",
                                             trunk.size = 0.5,
                                             branch.size = 2,
                                             twig.size = 0.5,
                                             alpha = 0.2,
                                             xlab = "Effect size (lnRR)", 
                                             fill =  T) +
  scale_fill_manual(values = "#98C127") +
  scale_colour_manual(values = "#98C127" ) +
    scale_y_continuous(limits = c(-0.7, 0.7)) +
theme_minimal(base_size = 14) +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
    legend.position = c(0.98, 0.05),
    legend.justification = c(1, 0),
    legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_blank()
  ) +
  labs(x = "Intercept")

# Plot for SMDH
intercept_SMDH_plot_crop <- orchaRd::orchard_plot(intercept_SMDH,
                                    mod = "1",
                                    group = "paper_ID",
                                    trunk.size = 0.5,
                                    branch.size = 2,
                                    twig.size = 0.5,
                                    alpha = 0.2,
                                    xlab = "Effect size (SMDH)",
                                    fill = TRUE) +
  scale_fill_manual(values = "#F47A00") +
  scale_colour_manual(values = "#F47A00") +
  scale_y_continuous(limits = c(-2.7, 2.7)) +
  theme_minimal(base_size = 14) +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
    legend.position = c(0.98, 0.05),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_blank()
  ) +
  labs(x = "Intercept")

# Combine using patchwork
Figure_intercept_crop <- intercept_lnRR_plot_crop / intercept_SMDH_plot_crop +
  plot_annotation(tag_level = c("A","B"))

ggsave(here::here("figures/Figure_overall_effect_crop.png"), plot = Figure_intercept_crop, height = 150, width = 170, units = "mm", dpi = 600)
```

# Hypothesis meta-regression

```{r orchard plot hypothesis meta-regression}

# Loading models for SMDH and lnRR

lnRR_hypothesis<-readRDS(here::here("model/lnRR_hypothesis.rds"))
SMDH_hypothesis<-readRDS(here::here("model/SMDH_hypothesis.rds"))

# Plot lnRR meta-regression on hypothesis

lnRR_hypothesis_plot <-
  orchard_plot(mod_results(lnRR_hypothesis,
                           mod = "Hypothesis",
                           group = "paper_ID"),
               trunk.size = 0.25,
               branch.size = 1,
               twig.size = 0.5,
               alpha = 0.4,
               xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  labs(x = "",
       y = "Effect size (lnRR)")+
  theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.05),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
  scale_x_discrete(labels = c("Both","Courtship","Parental Care"))

# Plot SMDH meta-regression on hypothesis

SMDH_hypothesis_plot <-
  orchard_plot(
    mod_results(
      SMDH_hypothesis,
      mod = "Hypothesis",
      group = "paper_ID"
    ),
    trunk.size = 0.25,
    branch.size = 1,
    twig.size = 0.5,
    alpha = 0.4,
    xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  labs(x = "",
       y = "Effect size (SMDH)")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.05),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
  scale_x_discrete(labels = c("Both","Courtship","Parental Care"))

@@

# Combine using patchwork
Figure_hypothesis <- lnRR_hypothesis_plot + SMDH_hypothesis_plot +
  plot_annotation(tag_level = c("A","B"))

ggsave(here::here("figures/Figure_hypothesis.png"), plot = Figure_hypothesis, height = 120, width = 250, units = "mm", dpi = 600)

##-----------------------------------------------------------------------------

# Now the cropped figures for the main manuscript

##-----------------------------------------------------------------------------

# Plot lnRR meta-regression on hypothesis

>>>>

## Visualising location and bird species

For visualising purposes we use adapt code by [Mentesana, Hau, D'Amelio, Adreani, & Sánchez-Tójar, (2025)](https://doi.org/10.1111/ele.70100), available on the accompanying [GitHub repository](https://github.com/ASanchez-Tojar/meta-analysis_egg_hormones_and_fitness/blob/main/code/003_figures.R).

The following code chunk is used to set up the workspace and load (or install) all required packages to replicate the generatation of figures and tables presented in our manuscript.

```{r load packages, message=FALSE, warning=FALSE}
## Setting up workspace using pacman
if (!requireNamespace("pacman", quietly = TRUE)) {
  install.packages("pacman")
}

## installing orchaRd from GitHub
if (!requireNamespace("orchaRd", quietly = TRUE)) {
  ## installing orchaRd from GitHub
  pacman::p_install_gh("daniel1noble/orchaRd", ref = 'main')
}

## Install/load required packages
pacman::p_load(
  cowplot,
  ggraph, # visualising author network
  gt, # suppl 
  here,
  igraph, # visualising author network
  maps,
  metafor,
  orchaRd,
  patchwork,
  purrr,
  tidyverse)
```

For the purpose of this map, longitude and latitude of the study area manually added to the dataset. They are saved to `dataset_analysis$population_location` as they were extracted from the respective papers. If not provided by the authors, a general location was manually selected. Note, coordinates are used for visualising only.

* Load datasets

```{r location-map}
## Load data for plotting a location map
## -----------------------------------------------------------

# Loading cleaned dataset
dataset_analysis <- read_csv(here::here("data/04_data_analysis/dataset_analysis.csv"))

## Split population_ID into location and country
dataset_analysis[c('Location','Country')] <- str_split_fixed(dataset_analysis$population_ID, ',', 2)

## set coordinates for sampling locations
data_coordinates <- data.frame(
  Location = unique(dataset_analysis$Location),
  Lat_Location = c(51.50, 38.41, 40.45, 45.40, 52.39, 37.18,
                   40.53, 54, 39.05, 51.57, 48, 42.54, 39.95,
                   40.13,28.10,52.06,60.39),
  Long_Location = c(19.29,-9.02,-3.50, -64.10, 6.05, -3.11,
                    -4.01, -124, -76.81, -2.26, 11, 8.91,
                    -75.16, -8.27, 107.10, 8.25, 5.32))

## Let's now merge the datasets by the location names
dataset_analysis <- dataset_analysis %>%
  left_join(data_coordinates, by = "Location")

## Count how many times each Location appears in the full dataset
location_counts <- dataset_analysis %>%
  group_by(Location, bird_species) %>%
  summarise(size.freq = n())

@@

# create world map using ggplot() function 
# geom_map() function takes world coordinates as input to plot world map 
fig_map <- ggplot(world_coordinates, aes(x = long, y = lat)) + 
  geom_map(map = world_coordinates, 
           aes(map_id = region), 
           color = "white", fill = "#D9EAF7") + 
  geom_point(data = dataset_analysis_unique_rows, 
             aes(x = Long_Location, y = Lat_Location,
                 size = size.freq, colour = bird_species),
             alpha = 0.6) +
  scale_size(range = c(1, 2.5)) +
  scale_fill_manual(values = c("#00B0BE","#FFB255",  "#FF8CAE", 
                               "#F47A00", "#98C127","#003A7D","#7E4794")) +

  scale_colour_manual(values = c("#00B0BE","#FFB255",  "#FF8CAE", 
                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
  guides(size = "none", alpha = "none",
         colour = guide_legend(override.aes = list(size = 1.5), keywidth = 0.4,
                               keyheight = 0.4)) +
  labs(x = "Longitude",
       y = "Latitude",
       col = "Bird Species") +
  theme_classic() +
  theme(plot.margin = margin(t = 15, r = 15, b = 5, l = 5),  
        legend.position = c(1.02, 0.42),
        legend.justification = c("right", "bottom"),
        legend.background = element_rect(fill = "white", color = "black"),
        legend.text = element_text(size = 6),
        legend.title = element_text(size = 7),
        axis.title = element_text(size = 8),
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10))

# To add the zoomed in map.. to show the points more clearly
zoom_map <- ggplot() + 
  geom_map(data = world_coordinates, map = world_coordinates,
           aes(map_id = region),
           color = "white", fill = "#D4D4D4") +
  geom_point(data = dataset_analysis_unique_rows,
             aes(x = Long_Location, y = Lat_Location,
                 size = size.freq, colour = bird_species),
             position = position_jitter(width = 0.2, height = 0.2),
             alpha = 0.7) +
  scale_size(range = c(1, 2)) +
  scale_colour_manual(values = c("#00B0BE","#FFB255",  "#FF8CAE", 
                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
  coord_cartesian(xlim = c(-10, 20), ylim = c(25, 65)) +  # Northern Hemisphere
  theme_void() +
  theme(legend.position = "none",
        plot.background = element_rect(color = "white", fill = "white"),
        panel.border = element_rect(colour = "black", fill = NA, size = 1))

geographic_distribution <- ggdraw() +
  draw_plot(fig_map) +
  draw_plot(zoom_map, x = 0.11, y = 0.21, width = 0.20, height = 0.28) +
  theme(panel.border = element_rect(colour = "black", fill = NA, size = 1.2))

print(geographic_distribution)
```

```{r, eval=FALSE}
## Save image file
ggsave(here::here("figures/Figure_Distribution.png"),
       plot = geographic_distribution, height = 100, width = 170, units= 'mm', dpi = 600)
```

## Visualizing author network

```{r author-network, eval=FALSE}
# Sun Aug 31 19:25:52 2025 ------------------------------
# Show code, but eval = FALSE

## Loading cleaned dataset
# Sun Aug 31 19:26:35 2025 ------------------------------
# The folliwing file is not found, assume same as above?!
# dataset_analysis<- read_csv(here::here("data/03_data_cleaning/dataset_analysis.csv"))

clean_author <- function(name) {
  name %>%
    str_replace_all(",", "") %>%   # remove commas
    str_squish() %>%              # remove excess whitespace
    str_to_title()                # standardize case (optional, if needed)
}

# Apply cleaning to first and last author fields
author_roles <- dataset_analysis %>%
  distinct(paper_ID, .keep_all = TRUE) %>%
  select(paper_ID, authors, bird_species) %>%
  mutate(
    author_list = str_split(authors, ";\\s*"),
    first_author = map_chr(author_list, 1),
    last_author = map_chr(author_list, ~ tail(.x, 1))
  ) %>%
  mutate(
    first_author=case_when(
      first_author == "Polo, V" | first_author == "Polo V" ~ "Polo V.",
      first_author == "Soler J J" ~ "Soler J. J.",
      first_author == "Glądalski, M" ~ "Gladalski M.",
      first_author == "Gwinner, H" | first_author == "Gwinner H" ~ "Gwinner H.",
      TRUE ~ as.character(first_author)
    )) %>%
  mutate(
    last_author=case_when(
      last_author == "Veiga J P" ~ "Veiga J. P.",
      TRUE ~ as.character(last_author)
    )
  )

# 2. Create Core Author Pairs (First → Last)
author_pairs_core <- author_roles %>%
  select(paper_ID, first_author, last_author) %>%
  rename(from = first_author, to = last_author) %>%
  filter(from != to) %>%
  count(from, to, name = "weight")

# 3. Build Author Graph
author_graph <- graph_from_data_frame(author_pairs_core, directed = TRUE)

# 4. Assign Dominant Bird Species to PIs (last authors)
author_species <- author_roles %>%
  select(last_author, bird_species) %>%
  group_by(last_author, bird_species) %>%
  count() %>%
  slice_max(n, n = 1) %>%
  distinct(last_author, .keep_all = TRUE)

# Add species as vertex attribute
V(author_graph)$bird_species <- author_species$bird_species[
  match(V(author_graph)$name, author_species$last_author)
]

# 5. Optional: Scale node size by number of papers per author
author_paper_counts <- author_roles %>%
  pivot_longer(cols = c(first_author, last_author), names_to = "role", values_to = "author") %>%
  count(author, name = "paper_count")

# Add paper count attribute
V(author_graph)$paper_count <- author_paper_counts$paper_count[
  match(V(author_graph)$name, author_paper_counts$author)
]

# Replace NAs with small size for isolated authors
V(author_graph)$paper_count[is.na(V(author_graph)$paper_count)] <- 1

# 6. Plot with ggraph
ggraph(author_graph, layout = "fr") +
  geom_edge_link(aes(width = weight), alpha = 0.4, color = "grey50") +
  geom_node_point(aes(color = bird_species, size = paper_count)) +
  geom_node_text(aes(label = name), repel = TRUE, size = 3) +
  scale_edge_width(range = c(0.3, 2)) +
  scale_size(range = c(3, 10)) +
  theme_void() +
  labs(title = "Author Collaboration Network by Bird Species",
       size = "Paper Count") +
  theme(legend.position = "right")
```

## Intercept only model

@@

```{r orchard plot for intercept only models}
# Loading models for SMDH and lnRR
intercept_lnRR <- readRDS(here::here("model/intercept_lnRR.rds"))
intercept_SMDH <- readRDS(here::here("model/intercept_SMDH.rds"))

# Plot for lnRR
intercept_lnRR_plot <- orchaRd::orchard_plot(
  intercept_lnRR,
  mod = "1",
  group = "paper_ID",
  trunk.size = 0.3,
  branch.size = 2,
  twig.size = 0.5,
  alpha = 0.2,
  xlab = "Effect size (lnRR)", 
  fill =  T,
  k.pos = c(0.53,0.6,0.6)) +
  scale_fill_manual(values = "#98C127") +
  scale_colour_manual(values = "#98C127" ) +
  theme_minimal(base_size = 14) +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
    legend.position = c(0.98, 0.05),
    legend.justification = c(1, 0),
    legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_blank()) +
  labs(x = "Intercept")

# Plot for SMDH
intercept_SMDH_plot <- orchaRd::orchard_plot(
  intercept_SMDH,
  mod = "1",
  group = "paper_ID",
  trunk.size = 0.3,
  branch.size = 2,
  twig.size = 0.5,
  alpha = 0.2,
  xlab = "Effect size (SMDH)",
  fill = TRUE,
  k.pos = c(2,0.6,0.6)) +
  scale_fill_manual(values = "#F47A00") +
  scale_colour_manual(values = "#F47A00") +
  theme_minimal(base_size = 14) +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
    legend.position = c(0.98, 0.05),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_blank()
  ) +
  labs(x = "Intercept")

# Combine using patchwork
Figure_intercept <- intercept_lnRR_plot / intercept_SMDH_plot +
  plot_annotation(tag_level = c("A","B"))
print(Figure_intercept)
```

```{r figures/Figure_overall_effect.png, eval=FALSE}
## save image file
ggsave(here::here("figures/Figure_overall_effect.png"), 
       plot = Figure_intercept, height = 150, width = 170, units = "mm", dpi = 600)
```

Now the crop the figure as presented in the main manuscript

```{r orchard plot for intercept only models; manuscript file}
intercept_lnRR_plot_crop <- orchaRd::orchard_plot(
  intercept_lnRR,
  mod = "1",
  group = "paper_ID",
  trunk.size = 0.5,
  branch.size = 2,
  twig.size = 0.5,
  alpha = 0.2,
  xlab = "Effect size (lnRR)", 
  fill =  T,
  k.pos = c(0.53,0.6,0.6)) +
  scale_fill_manual(values = "#98C127") +
  scale_colour_manual(values = "#98C127" ) +
  scale_y_continuous(limits = c(-0.6, 0.6)) +
  theme_minimal(base_size = 14) +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
    legend.position = c(0.98, 0.05),
    legend.justification = c(1, 0),
    legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_blank()) +
  labs(x = "Intercept")

# Plot for SMDH
intercept_SMDH_plot_crop <- orchaRd::orchard_plot(
  intercept_SMDH,
  mod = "1",
  group = "paper_ID",
  trunk.size = 0.5,
  branch.size = 2,
  twig.size = 0.5,
  alpha = 0.2,
  xlab = "Effect size (SMDH)",
  fill = TRUE,
  k.pos = c(2,0.6,0.6)) +
  scale_fill_manual(values = "#F47A00") +
  scale_colour_manual(values = "#F47A00") +
  scale_y_continuous(limits = c(-2.3, 2.3)) +
  theme_minimal(base_size = 14) +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
    legend.position = c(0.98, 0.05),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_blank()) + labs(x = "Intercept")

# Combine using patchwork
Figure_intercept_crop <- intercept_lnRR_plot_crop / intercept_SMDH_plot_crop +
  plot_annotation(tag_level = c("A","B"))
print(Figure_intercept_crop)
```

```{r figures/Figure_overall_effect_crop.png, eval=FALSE}
## save image file 
ggsave(here::here("figures/Figure_overall_effect_crop.png"), 
       plot = Figure_intercept_crop, height = 150, width = 170, units = "mm", dpi = 600)
```

## Hypothesis meta-regression

```{r orchard plot hypothesis meta-regression}
# Loading models for SMDH and lnRR
lnRR_hypothesis <- readRDS(here::here("model/lnRR_hypothesis.rds"))
SMDH_hypothesis <- readRDS(here::here("model/SMDH_hypothesis.rds"))

# Plot lnRR meta-regression on hypothesis
lnRR_hypothesis_plot <- orchard_plot(mod_results(
  lnRR_hypothesis,
  mod = "Hypothesis",
  group = "paper_ID"),
  trunk.size = 0.25,
  branch.size = 1,
  twig.size = 0.5,
  alpha = 0.4,
  xlab = "") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  labs(x = "",
       y = "Effect size (lnRR)") +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.01),
    legend.background = element_blank(),
    legend.key = element_blank(),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)) + 
  scale_x_discrete(labels = c("Both","Courtship","Parental Care"))

# Plot SMDH meta-regression on hypothesis
SMDH_hypothesis_plot <- orchard_plot(mod_results(
  SMDH_hypothesis,
  mod = "Hypothesis",
  group = "paper_ID"),
  trunk.size = 0.25,
  branch.size = 1,
  twig.size = 0.5,
  alpha = 0.4,
  xlab = "") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  labs(x = "", y = "Effect size (SMDH)") +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.01),
    legend.background = element_blank(),
    legend.key = element_blank(),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)) + 
  scale_x_discrete(labels = c("Both","Courtship","Parental Care"))

@@

# Combine using patchwork
Figure_hypothesis <- lnRR_hypothesis_plot + SMDH_hypothesis_plot +
  plot_annotation(tag_level = c("A","B"))
print(Figure_hypothesis)
```

```{r figures/Figure_hypothesis.png, eval=FALSE}
## save image file 
ggsave(here::here("figures/Figure_hypothesis.png"),
       plot = Figure_hypothesis, height = 120, width = 250, units = "mm", dpi = 600)
```

Now the cropped figures for the main manuscript

```{r orchard plot hypothesis meta-regression; MS fig}
# Plot lnRR meta-regression on hypothesis
lnRR_hypothesis_plot_crop <- orchard_plot(mod_results(
  lnRR_hypothesis,
  mod = "Hypothesis",
  group = "paper_ID"),
  trunk.size = 0.5,
  branch.size = 1.3,
  twig.size = 0.5,
  alpha = 0.4,
  fill = T,
  k.pos = c(0.4,0.6,0.6),
  xlab = "") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_y_continuous(limits = c(-0.6, 0.6)) +
  labs(x = "",
       y = "Effect size (lnRR)") +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
        legend.position.inside = c(0.99, 0.01),
        legend.justification = c(1, 0), 
        legend.direction = "horizontal",
        legend.background = element_blank(),
        legend.key = element_blank(),
        legend.title = element_text(size = 6),
        legend.text = element_text(size = 5),
        axis.title = element_text(size = 10),
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)) + 
  scale_x_discrete(labels = c("Both","Courtship","Parental\nCare"))
